---
title: "ggplot2"
author: "Toufic Mayassi"
date: "September 15, 2015"
output: html_document
---
# load the data

```{r}
counts_raw <- read.delim("data//counts-raw.txt.gz")
counts_norm <- read.delim("data//counts-norm.txt.gz")
```

#dplyr

```{r}
library("dplyr")
```



```{r}
research <- filter(counts_raw, articleType == "Research Article")


#ggplot2

```{r}
library("ggplot2")
```

```{r}
p <- ggplot(data = research, mapping = aes(x = pdfDownloadsCount,
                                           y = wosCountThru2011))
p + geom_point()
```

# Challenge 

```{r}
p <- ggplot(data = research, mapping = aes(x = daysSincePublished,
                                           y = wosCountThru2011)) + geom_point(aes(color = journal), alpha = 0.5) + geom_smooth(color = "red")

p
```

# controlling the plot scales

```{r}
p <- ggplot(research, aes(x = pdfDownloadsCount,
                          y = wosCountThru2011)) +
  geom_point(aes(color = journal)) +
  geom_smooth()
p

p + scale_x_log10() + scale_y_log10()
```

# scales challenge 

```{r}
p <- ggplot(research, aes(x = sqrt(pdfDownloadsCount),
                          y = sqrt(wosCountThru2011))) + geom_point(aes(color = journal)) +
  geom_smooth() + 
  scale_color_brewer(palette = "Accent")
p
```

# subplots with facets

```{r}
p + facet_wrap(~journal)
```

# geoms challenge (I Couldnt get it)

```{r}
research <- mutate(research, mean = backtweetsCount/journal)
```

